\documentclass{article}

\begin{document}

\section{Stakeholders} 
Stakeholders are those who may be affected by or have an effect in the Artibot project. Identifying and understanding stakeholders will give more ideas we can work on. But the most important aspect is to increase the credibility and understandability of their interest. 

\section{Active Stakeholders} 

Active stakeholders are stakeholders that are directly affected by our project. 
•	University of Southeast Norway (USN) is one of our active stakeholder.
The university is providing us with equipment, components, the budget and the administrative tasks. In addition professors are directly connected to the university which in this case have roles some supervisors for our project. Finally the active product owner has a direct influence over our project provided from the university. 

•	Artibot team members are key stakeholders in this project. 

•	Investors play an active role to our project by proving with financial investments. Investors want a profitable outcome of our project. 

Passive Stakeholders
Passive stakeholders have indirect relations to the Artibot project
•	Suppliers count as a secondary or passive stakeholder. In this case Nvidia is our main supplier of the TX2 module which is used to control the RC car. 

Key Stakeholders 
Both the active project owner and the USN have been defined as Artibots key stakeholder since these stakeholders have something to gain in our projects success. 

Overview of stakeholders
 
	
Personals	Role	Contact
Aurilla Aurelie Arntzen	Active Project Owner 	Aurilla.Aurelie.Arntzen@usn.no

\end{document}